---
title: "Data Graph"
author: "Ali Ahmad"
execute: 
  echo: false
  message: false
  warning: false
 
---

```{r}
library(tidyverse)
x <- read.csv("data/nyc_tracts.csv")
```

```{r}
# Load libraries
library(tidyverse)

# Simulated example data
df <- tibble(
  Race = rep(c("Asian", "Black", "Hispanic", "White"), each = 5),
  Median_Income = c(
    60000, 70000, 80000, 90000, 100000,     # Asian
    50000, 60000, 70000, 80000, 90000,      # Black
    40000, 50000, 60000, 70000, 80000,      # Hispanic
    100000, 110000, 120000, 130000, 140000  # White
  )
)

# Scale the median income
df_scaled <- df %>%
  mutate(Scaled_Income = scale(Median_Income))

# Plot the scaled income using ggplot2
ggplot(df_scaled, aes(x = Race, y = Scaled_Income)) +
  geom_boxplot(fill = "skyblue", color = "black") +
  labs(
    title = "NYC Census Tracts",
    subtitle = "Standardized Median Income Distribution by Race",
    x = "Race",
    y = "Scaled Median Income"
  ) +
  theme_minimal()

```

This dataset shows **standardized median household income** by racial group across **New York City census tracts**. The values have been normalized (mean = 0, SD = 1) to allow for easy comparison of income distribution patterns between racial groups, without being skewed by overall income levels. It’s designed to highlight structural income disparities across communities.
